### 2021-12-19 documentos/kraus.tex
dandole

Any PCE channel can be seen as the fixed point of some decoherence process. We will show this first for PCEGs. Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
\end{align}
where $\gamma>0$. It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec \alpha, t}$, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.

Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process. For them, the Lindblad generators are simply the sum of the Lindbladians of the corresponding generators. As an example, consider the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation process described with the following Lindbladian,
\begin{equation}
\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}+\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho \right)}{2},
\end{equation}
where $\gamma_{(0,3)}$ and $\gamma_{(3,3)}$ are positive and correspond to the Lindblad operators $\sigma_{(0,3)}$ and $\sigma_{(3,3)}$. Notice that such election of Lindblad operators is not unique, as the PCE channel described here is also equal to $\mcG_{(0,3)}\mcG_{(3,0)}$.

In addition to the implementation via decoherence processes, PCE channels can also be described with collision models [cita]. To see this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla [Stinespring citation]. For any PCEG, a qubit can always be chosen as the ancilla, concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed. In fact, generators are described with one collision. For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$. For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit environment with the additional assumption that its state is erased and transformed again $\ket{0}$ after each collision). The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
$U_{\vec\alpha_M}U_{\vec\alpha_{M-1}}\dots U_{\vec\alpha_1}$
Described as the system \textit{colliding} with qubit particles
\begin{itemize}
\item Relate to decoherence, for PCEG
\item Play with non PCEG PCEs
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}

>>>>

Any PCE channel can be seen as the fixed point of some decoherence process. We will show this first for PCEGs. Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
\end{align}
where $\gamma>0$. It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec \alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.

Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process. For them, the Lindblad generators are the sum of the Lindbladians of the corresponding generators. As an example, consider the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation process described with the following Lindbladian,
\begin{equation}
\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}+\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho \right)}{2},
\end{equation}
where $\gamma_{(0,3)}$ and $\gamma_{(3,3)}$ are positive and correspond to the Lindblad operators $\sigma_{(0,3)}$ and $\sigma_{(3,3)}$. Notice that such election of Lindblad operators is not unique, as the PCE channel described here is also equal to $\mcG_{(0,3)}\mcG_{(3,0)}$.

PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}. To prove this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla~\cite{Stinespring2006}. Since PCEG always have Kraus rank $2$, one can always choose a qubit as the ancillary system, concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as,
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed. In fact, generators are described with one collision. For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$. For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision). The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
\begin{itemize}
\item Relate to decoherence, for PCEG
\item Play with non PCEG PCEs
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}
